Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2018-07-17 ms.tex

Figure~\ref{fig:panel1}, at XX Myr, shows each just after the first few SN in each simulation. Already there are significant differences across runs. Gas outside the galaxy is warm ($\sim$~10$^{4}$~K) and ionized out to XX~pc above/below the plane of the disk in our fiducial run. This same gas is cold ($<10^4$~K) and neutral in both other runs. As a result, the SNe in each are contained, creating very hot diffuse bubbles contained by colder, denser shells close to the disk. These mass and energy from the SNe in our fiducial run readily escape the galaxy through the channels of diffuse, ionized gas carved out by long-range stellar radiation feedback.

\begin{figure*}
\centering
\includegraphics[width=0.99\linewidth]{comparison_panel}
\caption{\textbf{In the final version of this figure I will add labels for each row marking the simulation, and a line giving the scale of each figure.}}
\label{fig:pane1l}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.99\linewidth]{comparison_panel2}
\caption{Panel}
\label{fig:pane2}
\end{figure*}

>>>>

Figure~\ref{fig:panel1}, at XX Myr, shows each just after the first few SN in each simulation. Already there are significant differences across runs. Gas outside the galaxy is warm ($\sim$~10$^{4}$~K) and ionized up to XX~pc above/below the plane of the disk in our fiducial run. This same gas is cold ($<10^4$~K) and neutral in both other runs. The contrast between the fiducial and shortrad radiation is seen most clearly in the ionized region in-plane and to the right of center in the top and bottom panels. This region contains massive stars that are capable of generating enough ionizing radiation to carve a channel out to the halo of our fiducial simulation; by construction, this does not occur in the shortrad case. The warm / ionized feature towards the center of each galaxy is gas from a recent SN. This is much more well contained and hotter in the noRT and shortrad runs than in our fiducial simulation.

\begin{figure*}
\centering
\includegraphics[width=0.99\linewidth]{DD0136_fiducial_shortrad_nort}
\caption{\textbf{In the final version of this figure I will add labels for each row marking the simulation, and a line giving the scale of each figure.}}
\label{fig:pane1l}
\end{figure*}

As these simulations evolve, the existence of these diffuse, ionized channels in the fiducial run easily allow significant outflows from SNe to escape the disk and move well into the halo of our galaxy. In contrast, the same SNe in the other two simulations are well contained, surrounded by shells of denser, neutral gas and unable to driving significant mass loss from the galaxy. In the noRT case, outflow does eventually develop, but it takes the factor of 5 increase in SFR for SN gas to finally break out from the neutral gas surrounding the galaxy.

\begin{figure*}
\centering
\includegraphics[width=0.99\linewidth]{DD0160_fiducial_shortrad_nort}
\caption{Panel}
\label{fig:pane2}
\end{figure*}
